Opening the era of quasar host studies at high redshift with JWST

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/paper submit/submit/apjl_source_file/ding_jwst_v1.tex
For ceers and upcoming data

\documentclass[twocolumn]{aastex631}
\usepackage{amsmath}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

@@

\newcommand{\org}[1]{\textcolor{orange}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\tbd}[1]{\textcolor{red}{[{\bf TBD}: #1]}}

@@

\begin{abstract}
We measure the host galaxy properties of five quasars with $z\sim 1.6 - 3.5$ selected from SDSS and AEGIS, which fall within the \jwst/\hst\ CEERS survey area. A PSF library is constructed based on stars in the full field-of-view of the data and used with a 2-dimensional image modeling tool \galight\ to decompose the quasar and its host with multi-band filters available for \hst\ ACS+WFC3 and \jwst\ NIRCAM (12 filters covering \hst\ F606W to \jwst\ F444W). As demonstrated, \jwst\ provides the first capability to detect quasar hosts at $z>3$ and enables spatially-resolved studies of the underlying stellar populations at $z\sim2$ within morphological structures (spiral arms, bar) not possible with \hst. Overall, we find quasar hosts to be disk-like, lack merger signatures, and have sizes generally more compact than typical star-forming galaxies at their respective stellar, thus in agreement with results at lower redshifts. The fortuitous face-on orientation of SDSSJ1420+5300A at $z = 1.646$ enables us to find higher star formation and younger ages in the central $2-4$ kpc region relative to the outskirts, which may help explain the relatively compact nature of quasar hosts and pose a challenge to AGN feedback models.

@@

To make further progress, a decomposition of the host galaxy from its central quasar is required to measure the host properties at earlier cosmic times ($z\gtrsim2$) when the central regions of galaxies are forming stars and particularly those that can be spatially resolved. At a cosmological distance, galaxies have smaller apparent sizes and become fainter due to cosmological surface dimming. The unresolved quasars as bright point sources can outshine the host galaxy, which makes the decomposition of the host challenging, even with {\it Hubble Space Telescope} (\hst) WFC3-IR, which has excelled at $z < 2$. Owing to this reason, most of the studies in the literature so far have been focused on the moderate-luminosity AGNs whose brightness is comparable to their host ~\citep{Park15, Tre++07, Bennert11, Woo++08, Jah++09, SS13, Mechtley2016,Ding2020, Ding2021, 2021ApJ...906..103L}. Hence, the stellar content of the luminous AGN hosts at $z>2$, which harbors the most massive SMBHs, has not yet been studied.

The {\it James Webb Space Telescope} (\jwst) opens up a new opportunity to extend the study of quasar hosts at high-$z$. The infrared coverage at $\lambda > 2 \mu$m provides the ability to probe the galaxy 4000~\angstrom\ break beyond $z\sim 3.5$.  The unprecedented sensitivity and resolution by \jwst\ will be a key to separating the unresolved quasar component from the extended emission of its host galaxy, particularly due to the larger aperture compared to \hst\ and the stability of the telescope, which effectively improves the characterization of the PSF.

In this paper, we use deep \textit{Near Infrared Camera} \citep[NIRCam,][]{Rieke05} imaging data from the \jwst\ Cosmic Evolution Early Release Science\footnote{\url{https://ceers.github.io}}~\citep[CEERS,][]{CEERS} program to decompose the optical and infrared emission from five quasars with redshift between 1.6 and 3.5. We limit the AGN sample to those with spectroscopic redshifts to provide accurate stellar masses and sizes of their host galaxies. We will carry out an AGN decomposition to reveal the host galaxy and then perform the spectral energy distribution (SED) fitting to infer the stellar mass, star formation rate (SFR), and stellar age. These results will aid in our ability to establish relations between AGN and host galaxy formation with \jwst\ \citep{Kocevski2022}.

The paper is organized as follows. In Section~\ref{sec:design}, we describe the \jwst/\hst\ data and our sample selection. We introduce our decomposition method in Section~\ref{sec:decomp}, including our PSF library construction, decomposition tool, and SED fitting. In Section~\ref{sec:result}, we present our measurement result and compare the inferred size mass relations with the ones from the literature. The concluding remarks are presented in Section~\ref{sec:conclusion}. Magnitudes are given in AB System. A Chabrier initial mass function is employed to measure the galaxy's stellar mass for consistency. We use a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

@@

\subsection{CEERS survey imaging and data reduction}
The CEERS \jwst\ early release science program (ERS Program \#1345) is designed to cover 100 arcmin$^2$ of the AEGIS fields with imaging and spectroscopic data~\citep{CEERS}. This program will observe ten pointings with \jwst/NIRCam as parallel with primary fields to be taken with NIRSpec and MIRI. In late June 2022, four pointings  (CEERS1, CEERS2, CEERS3, and CEERS6) were completed using 7 NIRCam filters: F115W, F150W, F200W, F277W, F356W, F410M, and F444W. The integration times are 2,635 seconds for each filter, with the exception of F115W, which was taken with an exposure time twice as long. For the CEERS2 pointing, one additional visit is performed with a slightly different PA and positional offset using filters F200W and F444W. We refer the reader to~\citet{Finkelstein2022} for more details on the \jwst\ observations and survey design.

\begin{figure*}
\centering
\includegraphics[trim={3cm 0cm 3cm 0cm},clip,width=1.8\columnwidth]{figures/psfs_profile.pdf}
\caption{Selected nine PSF surface brightness (SB) profiles (annuli) as a function of radius (based on stars detected by \jwst) per filter are shown selected from our PSF library compared with the simulated PSF model by \texttt{webbpsf}. The vertical lines indicate the FWHM values of the PSF-stars (averaged) and PSF model by \texttt{webbpsf}. We only show the profile's very inner region ($<7$ pixels), which is the key to the AGN subtraction. The PSFs in our library demonstrate a very stable performance, while the simulated PSF models by \jwst\ are too narrow (i.e., peaking at the center) for all the filters.
\label{fig:PSFprofile}}
\end{figure*}

 We performed our own data reduction to achieve science-quality images. The archived data products (stage 2) were acquired from the STScI MAST Portal\footnote{\url{https://archive.stsci.edu/}}. The stage 2 data were processed by the \jwst\ pipeline version 1.5.3 with the mapping file \textsf{jwst\_0942.pmap} except for F410M and F444W. Depending on the fields, we use \textsf{jwst\_0877.pmap} and \textsf{jwst\_0878.pmap} for F410M. For F444W, we use \textsf{jwst\_0877.pmap}, \textsf{jwst\_0878.pmap} and \textsf{jwst\_0881.pmap}. Due to the known issue for the background subtraction with the v.1.5.3 pipeline, we further post-process the stage 2 images as follows. We first subtracted the background light using \texttt{photutils} based on \textsf{Background2D} function. 
 The so-called $1/f$ noise pattern due to detector read noise was removed with the code provided by the CEERS team\footnote{\url{https://ceers.github.io/releases.html\#sdr1}}.

We then use the \jwst\ stage 3 pipeline to produce the individual images. In the  \textsf{Resample} step, we increase the pixel resolution by a factor of two with the drizzle algorithm. The pixel scale for the long-wavelength (LW) filters is $\sim$ 0\farcs{}0315 and short-wavelength (SW) filters $\sim$ 0\farcs{}0156. Saturated pixels are labeled as empty in this process. For the purposes of building a PSF library (see Section~\ref{sec:psfLibrary}), we require all four CEERS fields to have the same rotation angle. Thus, we do not apply any rotations when drizzling the images. For WCS calibration, we use the GAIA DR3 source catalog\footnote{\url{https://gea.esac.esa.int/archive/}}~\citep{GAIA16} to align our image.

The conversion factor from the instrumental signal to physical units Mega-Janskys per steradian is based on the calibration files \textsf{jwst\_nircam\_photom\_0101.fits} for module A, and \textsf{jwst\_nircam\_photom\_0104.fits} for module B. This step requires a re-calibration to correct the original flux based on pre-flight measurements. A significant difference ($10\%-20\%$ flux level) between the pre-flight and post-flight photometric reference files is noted and mentioned in~\citet{Adams22}. We have updated our calibration for the F410M and F444W flux densities based on this information. Until today, the calibration file of \jwst\ still requires updating, and there is still up
%to 0.3 mag 
to 20\% uncertainty to conversion between the ADU and flux in filters.

For the \hst\ imaging, we adopt the datasets provided by CEERS collaboration\footnote{\url{https://ceers.github.io/hdr1.html\#hst-egs}}. These \hst\ images are observed from eight different \hst\ programs (10134, 12063, 12099, 12167, 12177, 12547, 13063 and 13792), with a total of 1,767 exposures. The data reduction follows the procedures described in~\citet{Koekemoer2011}. We adopt the filters including ACS/WFC F606W and F814W, and WFC3/IR F125W, F140W, and F160W. The final pixel scale has been drizzled to a 0\farcs{}03 for all bands.

\subsection{Sample Selection}
We searched for quasars in the SDSS DR16 quasar catalog~\citep{2020ApJS..250....8L} and the AEGIS-X AGN catalog~\citep{2009ApJS..180..102L, Nandra2015} that fall within the CEERS field. We also limited our targets to those with spectroscopic redshifts greater than 1.6 to focus on high redshift quasars, which have been challenging for \hst\ to detect their host. Three SDSS quasars were identified with redshifts at 1.646, 2.588, and 3.442, respectively. SDSS1419+5254 ($z=3.442$) falls in CEERS2 and thus has only two \jwst\ filters (i.e., F200W and F444W) available at this moment. From AEGIS-X, we also find four quasars with spectroscopic redshifts above $z>1.6$. After manually checking, we find that two of them are matched to SDSS quasars\footnote{After the manual confirmation, we find SDSS1419+5254 and AEGIS 585 are the same system;  SDSS1420+5300A and AEGIS 742 are the same system.}. As a result, two additional targets are selected with redshift at 2.317 and 3.465, respectively. While MIRI images were taken in parallel, no additional quasars were found. We note that only one quasar (AEGIS 482) is in common with a recent \jwst\ study of X-ray-selected AGN in CEERS \citep{Kocevski2022}. The properties of our five quasars are given in Table~\ref{table:sample}.

\section{Quasar-host image decomposition} \label{sec:decomp}
We use our previous 2D image modeling strategy, as fully presented in~\citet{Ding2020}, to perform the AGN decomposition. We first build a PSF library by searching for all point sources (i.e., stars) in the \jwst\ field of views (FOVs). We then perform the fitting of the main quasar target by using the 2D image modeling tool \galight~\citep{Ding2020, Ding2021a} and consider each PSF-star in the library. The final PSF will be chosen from the top-ranked fits as described below.

@@

In this paper, we use the previous strategy of~\citet{Ding2022} and collect all isolated, unsaturated PSF stars with sufficient signal-to-noise levels to build our PSF library. We use the PSF-pickers (the \texttt{find$\_$PSF()} function) provided by \galight\ (see next section~\ref{subsec:decomp} for details) to help us collect these objects having a point-like feature as our initial PSF candidates through all the \jwst/\hst\ filters in four CEERS visits. By sorting the FWHM values from low to high and manually viewing the local image stamps of each PSF candidate, we select the PSF candidates that are isolated and sharp. To build the library, we select at least 12 PSF stars for each filter.

It is also known that simulated PSF for \hst\ based on \texttt{TinyTim}~\citep{2011SPIE.8127E..0JK} is usually inaccurate (narrow) and not ideal for our goal of AGN decomposition~\citep[e.g.,][]{Mechtley2012}. In this work, we also test the effectiveness of \texttt{webbpsf}~\citep{2014SPIE.9143E..3XP} to generate the PSF model for \jwst\ but find that the simulated PSF is also too narrow compared with the PSF in the library \citep[see][for similar conclusions]{Ono2022}. We show the surface brightness profiles of PSF stars and the PSF by \texttt{webbpsf} as a function of the radius (in pixel unit) in Figure~\ref{fig:PSFprofile}.

\begin{figure*}
\centering
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_35.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_0.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_2.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_51.pdf}
\caption{Science-grade images (1st and 3rd columns) and the host galaxy images (2nd and 4th columns) for the four quasar targets at $z>2$ with F200W and F444W filters are presented. In each case, the host galaxy image (i.e., data minus quasar) is produced by subtracting the best-fit PSF. The redshift of each quasar is indicated in each panel. The pixel units are in Mega-Janskys per steradian (MJy/sr).
For the LW (e.g., F444W) filter, AEGIS 477 happens to be located at the edge of FOV in module B; only the right-side part of the quasar is observed.}
\label{fig:datahost}
\end{figure*}

@@

We use the \texttt{gsf} package~\citep{Morishita2019} to fit the broad-band spectral energy distributions (SEDs) to infer the host stellar mass and further properties of the stellar population (i.e., stellar age and SFR). 
Stellar templates of different ages are combined to generate galaxy SED templates. In this process, weights are assigned to each stellar template and fit as free parameters to produce the final galaxy templates.
The stellar metallicity is fixed and set to the solar value. Despite the well-known degeneracy between age and metallicity, there is little effect on the determination of the \smass. The star formation rate and age will then be obtained from the final best-fit template. Dust attenuation and stellar emission lines are also considered in our SED fitting model.

We only use the host magnitudes obtained by \jwst\ filters to perform our SED fitting since the reliability of host magnitudes from \hst\ is highly uncertain. 
The SED fitting also requires errors on the magnitudes, which are estimated using the scatter of the magnitude inference from the top-5 ranked PSFs fits. If the scatter is below 0.15 mag, we fix the uncertainty at this value to account for a reported systematic error. For AEGIS 482 and SDSS1419+5254, we adopt 0.4 mag for the error since their results are provided by a single PSF.
For our sample at $z>2$, seven \jwst\ filters cover above and below the 4000~\angstrom\ break; thus, the SED fitting should provide a reliable best-fit galaxy template. Unfortunately, SDSS1419 currently only has observations with F200W and F444W, both above the 4000~\angstrom\ break. The SED fits are presented in Figure~\ref{fig:sed_spec} with the exception of SDSS1419. We note that SDSS1420A at $z=1.646$ has a marginal detection with ACS/F814W. As a constraint, we use five times the inferred flux from the F814W filter to set up an upper limit on the SED fit to constrain the strength of the 4000~\angstrom\ break. The host stellar inference, including \smass, SFR, and age, is given at the end of Table~\ref{table:sample}.

We classify the quasar hosts into star-forming and quiescent galaxies using the rest-frame U-V and V-J colors inferred by our model SED fits as done in \citet{vdW+2014}. For reference, we plot galaxy samples from CANDELS~\citep{vdW+2012, vdW+2014} at the equivalent redshifts to our sample (i.e., $1.6<z<3.5$), see Figure~\ref{fig:sizemass} - left. The distribution shows that the quasar hosts are mainly located in a star-forming region. One quasar host is at the boundary, possibly indicating that the host galaxy is close to transitioning to a more quiescent state. Broadly, these results are consistent with numerous studies that demonstrate an association between AGN/quasar activity and ongoing star formation over a wide range of cosmic time.

@@

@@

SDSS1420A is an ideal laboratory to further study high-$z$ quasar hosts since spatially-resolved properties of the stellar population are feasible due to the angular extent of the host, being face-on, and the spatial resolution of multi-band \jwst\ observations. SDSS1420A is a very massive disk galaxy (\smass$\sim11.5~\log$ M$_{\odot}$), thus likely to be fully quenched on a short timescale and transition to a bulge-dominated galaxy. Here, our aim is to demonstrate new science capabilities enabled by \jwst. While larger samples will be required to make substantive claims, the CEERS observations of a small quasar sample can already provide further insight into the resolved properties of quasar hosts that have yet to be explored at this resolution.

@@

\jwst\ has ushered in a new era for which we are now able to study quasar hosts to even higher redshift ($z\sim6$ and beyond) and lower mass. This is crucial to probe epochs closer to the formation of massive galaxies and their supermassive BHs, thus better constraining theoretical models of their connection \citep{Volonteri2021, Ding2022}.

@@

\bibliography{jwst_hosts}{}
\bibliographystyle{aasjournal}

>>>>

\documentclass[twocolumn,]{aastex631}
\usepackage{amsmath}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

@@

\newcommand{\org}[1]{\textcolor{orange}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{\bf #1}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\tbd}[1]{\textcolor{red}{[{\bf TBD}: #1]}}

@@

\begin{abstract}
We measure the host galaxy properties of five quasars with $z\sim 1.6 - 3.5$ selected from SDSS and AEGIS, which fall within the \jwst/\hst\ CEERS survey area. A PSF library is constructed based on stars in the full field-of-view of the data and used with the 2-dimensional image modeling tool \galight\ to decompose the quasar and its host with multi-band filters available for \hst\ ACS+WFC3 and \jwst\ NIRCAM (12 filters covering \hst\ F606W to \jwst\ F444W). As demonstrated, \jwst\ provides the first capability to detect quasar hosts at $z>3$ and enables spatially-resolved studies of the underlying stellar populations at $z\sim2$ within morphological structures (spiral arms, bar) not possible with \hst. Overall, we find quasar hosts to be disk-like, lack merger signatures, and have sizes generally more compact than typical star-forming galaxies at their respective stellar mass, thus in agreement with results at lower redshifts. The fortuitous face-on orientation of SDSSJ1420+5300A at $z = 1.646$ enables us to find higher star formation and younger ages in the central $2-4$ kpc region relative to the outskirts, which may help explain the relatively compact nature of quasar hosts and pose a challenge to AGN feedback models.

@@

To make further progress, a decomposition of the host galaxy from its central quasar is required to measure the host properties at earlier cosmic times ($z\gtrsim2$) when the central regions of galaxies are forming stars and particularly those that can be spatially resolved. At cosmological distances, galaxies have smaller apparent sizes and become fainter due to surface brightness dimming. The unresolved quasars, seen as bright point sources, can outshine the host galaxy, which makes the decomposition of the host challenging, even with {\it Hubble Space Telescope} (\hst) WFC3-IR, which has excelled at $z < 2$. Owing to this reason, most of the studies in the literature so far have been focused on the moderate-luminosity AGNs whose brightness is comparable to their host ~\citep{Park15, Tre++07, Bennert11, Woo++08, Jah++09, SS13, Mechtley2016,Ding2020, Ding2021, 2021ApJ...906..103L}. Hence, the stellar content of the luminous AGN hosts at $z>2$, which harbors the most massive SMBHs, has not yet been studied.

The {\it James Webb Space Telescope} (\jwst) opens up a new opportunity to extend the study of quasar hosts at high-$z$. The infrared coverage at $\lambda > 2 \mu$m provides the ability to probe the galaxy 4000~\angstrom\ break beyond $z\sim 3.5$.  The unprecedented sensitivity and resolution by \jwst\ is key to separating the unresolved quasar component from the extended emission of its host galaxy, particularly due to the larger aperture compared to \hst\ and the stability of the telescope, which effectively improves the characterization of the PSF.

In this paper, we use deep \textit{Near Infrared Camera} \citep[NIRCam,][]{Rieke05} imaging data from the \jwst\ Cosmic Evolution Early Release Science\footnote{\url{https://ceers.github.io}}~\citep[CEERS,][]{CEERS} program to decompose the optical and infrared emission from five quasars with redshift between 1.6 and 3.5. We limit the AGN sample to those with spectroscopic redshifts to provide accurate stellar masses and sizes of their host galaxies. We carry out a quasar decomposition to reveal the host galaxy and then perform the spectral energy distribution (SED) fitting to infer the stellar mass, star formation rate (SFR), and stellar age. These results will aid in our ability to establish relations between AGN and host galaxy formation with \jwst\ \citep{Kocevski2022}.

The paper is organized as follows. In Section~\ref{sec:design}, we describe the \jwst/\hst\ data and our sample selection. We introduce our decomposition method in Section~\ref{sec:decomp}, including our PSF library construction, decomposition tool, and SED fitting. In Section~\ref{sec:result}, we present our measurements and compare to the size - mass relations of non-active galaxies from the literature. The concluding remarks are presented in Section~\ref{sec:conclusion}. Magnitudes are given in AB System. A Chabrier initial mass function is employed to measure the stellar mass of the host galaxies. We use a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

@@

\subsection{CEERS survey imaging and data reduction}
The CEERS \jwst\ early release science program (ERS Program \#1345) is designed to cover 100 arcmin$^2$ of the AEGIS fields with imaging and spectroscopic data~\citep{CEERS}. This program will observe ten pointings with \jwst/NIRCam, six with NIRSpec in parallel, and four with MIRI in parallel. In late June 2022, four pointings  (CEERS1, CEERS2, CEERS3, and CEERS6) were completed using 7 NIRCam filters: F115W, F150W, F200W, F277W, F356W, F410M, and F444W. The integration times are 2,635 seconds for each filter, with the exception of F115W, which was taken with an exposure time twice as long. For the CEERS2 pointing, one additional visit was performed with a slightly different PA and positional offset using filters F200W and F444W. We refer the reader to~\citet{Finkelstein2022} and the CEERS overview paper (Finkelstein et al. in prep) for more details on the \jwst\ observations and survey design including the positions of the three dither pattern. This information can also be found via the\dataset[DOI]{https://doi.org/10.17909/3pf0-8b20} information.

\begin{figure*}
\centering
\includegraphics[trim={3cm 0cm 3cm 0cm},clip,width=1.8\columnwidth]{figures/psfs_profile.pdf}
\caption{Surface brightness (SB) profiles (annuli) of nine select PSFs are shown as a function of radius (based on stars detected by \jwst) per filter and compared with the simulated PSF model from \texttt{webbpsf}. The vertical lines indicate the FWHM values of the PSF-stars (averaged) and PSF model by \texttt{webbpsf}. We only show the inner regions ($<7$ pixels) of these profiles which are key for quasar subtraction. The PSFs in our library demonstrate very stable performance, while the simulated PSF models by \jwst\ are too narrow (i.e., peaking at the center) for all the filters.
\label{fig:PSFprofile}}
\end{figure*}

 We performed our own data reduction to achieve science-quality images. The archived data products (stage 2) were acquired from the STScI MAST Portal\footnote{\url{https://archive.stsci.edu/}}. The stage 2 data were processed by the \jwst\ pipeline version 1.5.3 with the mapping file \textsf{jwst\_0942.pmap} except for F410M and F444W. Depending on the fields, we use \textsf{jwst\_0877.pmap} and \textsf{jwst\_0878.pmap} for F410M. For F444W, we use \textsf{jwst\_0877.pmap}, \textsf{jwst\_0878.pmap} and \textsf{jwst\_0881.pmap}. Due to the known issue with the background subtraction for the v.1.5.3 pipeline, we further post-process the stage 2 images as follows. We first subtracted the background light using \texttt{photutils} based on \textsf{Background2D} function. 
 The so-called $1/f$ noise pattern due to detector read noise was removed with the code provided by the CEERS team\footnote{\url{https://ceers.github.io/releases.html\#sdr1}}.

We then use the \jwst\ stage 3 pipeline to produce the individual images. In the  \textsf{Resample} step, we increase the pixel resolution by a factor of two with the drizzle algorithm. The pixel scale for the long-wavelength (LW) filters is $\sim$ 0\farcs{}0315 and short-wavelength (SW) filters $\sim$ 0\farcs{}0156. Saturated pixels are labeled as empty in this process. For the purposes of building a PSF library (see Section~\ref{sec:psfLibrary}), we require all four CEERS fields to have the same rotation angle. Thus, we do not apply any rotations when drizzling the images. For WCS calibration, we use the GAIA DR3 source catalog\footnote{\url{https://gea.esac.esa.int/archive/}}~\citep{GAIA16} to align the images.

The conversion factor from the instrumental signal to physical units Mega-Janskys per steradian is based on the calibration files \textsf{jwst\_nircam\_photom\_0101.fits} for module A, and \textsf{jwst\_nircam\_photom\_0104.fits} for module B. This step requires a re-calibration to correct the original flux based on pre-flight measurements. A significant difference ($10\%-20\%$ flux level) between the pre-flight and post-flight photometric reference files is noted and mentioned in~\citet{Adams22}. We have updated our calibration for the F410M and F444W flux densities based on this information. Until today, the calibration file of \jwst\ still requires updating, and there is still up
%to 0.3 mag 
to 20\% uncertainty in conversion between the ADU and flux in these filters. As a note, this reduced data was also effective in identifying a low-luminosity AGN candidate at $z=5$~\citep{2022arXiv220907325O}.

For the \hst\ imaging, we adopt the datasets provided by CEERS collaboration\footnote{\url{https://ceers.github.io/hdr1.html\#hst-egs}}. These \hst\ images are observed from eight different \hst\ programs (10134, 12063, 12099, 12167, 12177, 12547, 13063 and 13792), with a total of 1,767 exposures. The data reduction follows the procedures described in~\citet{Koekemoer2011}. We adopt the filters including ACS/WFC F606W and F814W, and WFC3/IR F125W, F140W, and F160W. The final pixel scale has been drizzled to 0\farcs{}03 for all bands.

\subsection{Sample Selection}
We searched for quasars in the SDSS DR16 quasar catalog~\citep{2020ApJS..250....8L} and the AEGIS-X AGN catalog~\citep{2009ApJS..180..102L, Nandra2015} that fall within the CEERS field. We also limited our targets to those with spectroscopic redshifts greater than 1.6 to focus on high redshift quasars, which have been challenging for \hst\ to detect their host. Three SDSS quasars were identified with redshifts at 1.646, 2.588, and 3.442, respectively. SDSS1419+5254 ($z=3.442$) falls in CEERS2 and thus has only two \jwst\ filters (i.e., F200W and F444W) available at the time. From AEGIS-X, we found four quasars with spectroscopic redshifts above $z>1.6$ with two of them matched to SDSS quasars\footnote{We find SDSS1419+5254 and AEGIS 585 are the same system;  SDSS1420+5300A and AEGIS 742 are the same system.}. As a result, two additional targets are selected with redshift at 2.317 and 3.465, respectively. While MIRI images were taken in parallel, no additional quasars were found. We note that only one quasar (AEGIS 482) is in common with a recent \jwst\ study of X-ray-selected AGN in CEERS \citep{Kocevski2022}. The properties of our five quasars are given in Table~\ref{table:sample}.

\section{Quasar-host image decomposition} \label{sec:decomp}
We use our previous 2D image modeling strategy, as fully presented in~\citet{Ding2020} and originally based on HST/WFC3 imaging of quasars at $z\sim1.5$, to perform the AGN decomposition. We first build a PSF library by searching for all point sources (i.e., stars) in the \jwst\ field of views (FOVs). We then perform the fitting of the main quasar target by using the 2D image modeling tool \galight~\citep{Ding2020, Ding2021a} and consider each PSF-star in the library. The final PSF will be chosen from the top-ranked fits as described below.

@@

We use the previous strategy %of~\citet{Ding2020} 
and collect all isolated, unsaturated PSF stars with sufficient signal-to-noise levels to build our PSF library. We use the PSF-pickers (\texttt{find$\_$PSF()} function) provided by \galight\ (see section~\ref{subsec:decomp} for details) to help us collect these objects having a point-like feature as our initial PSF candidates through all the \jwst/\hst\ filters in four CEERS visits. By sorting the FWHM values from low to high and manually viewing the local image stamps of each PSF candidate, we select the PSF candidates that are isolated and sharp. To build the library, we select at least 12 PSF stars for each filter.  Note that these PSFs are normalized to unity by \galight\ before fitting. We provide the positions of each object used to construct the PSFs for each filter through an online website\footnote{\url{https://github.com/dartoon/my_code/blob/master/share_data/PSF_library_info.txt}}.

It is also known that simulated PSF for \hst\ based on \texttt{TinyTim}~\citep{2011SPIE.8127E..0JK} is usually inaccurate (narrow) and not ideal for our goal of AGN decomposition~\citep[e.g.,][]{Mechtley2012}. In this work, we also test the effectiveness of \texttt{webbpsf}~\citep{2014SPIE.9143E..3XP} to generate the PSF model for \jwst\ but find that the simulated PSF is also too narrow compared with the empirical PSFs our the library \citep[see][for similar conclusions]{Ono2022}. We show the surface brightness profiles of PSF stars and the PSF by \texttt{webbpsf} as a function of radius (in pixel unit) in Figure~\ref{fig:PSFprofile}.

\begin{figure*}
\centering
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_35.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_0.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_2.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_51.pdf}
\caption{Science-grade images (1st and 3rd columns) and host galaxy images (2nd and 4th columns) for the four quasars at $z>2$ with F200W and F444W filters. In each case, the host galaxy image (i.e., data minus quasar) is produced by subtracting the best-fit PSF. The redshift of each quasar is indicated in each panel. The pixel units are in Mega-Janskys per steradian (MJy/sr).
For the LW (e.g., F444W) filter, AEGIS 477 happens to be located at the edge of FOV in module B; only the right-side part of the quasar is observed.}
\label{fig:datahost}
\end{figure*}

@@

We use the \texttt{gsf} package~\citep{Morishita2019} to fit the broad-band spectral energy distributions (SEDs) to infer the host stellar mass and further properties of the stellar population (i.e., stellar age and SFR). 
Stellar templates of different ages are combined to generate galaxy SED templates. In this process, weights are assigned to each stellar template and fit as free parameters to produce the final galaxy templates.
The stellar metallicity is fixed and set to the solar value. Despite the well-known degeneracy between age and metallicity, there is little effect on the determination of the \smass. The star formation rate and age will then be obtained from the final best-fit template. Dust attenuation and stellar emission lines are also considered in our SED fitting model. Note that the seven JWST filters together provide continuous wavelength coverage (see the filters' response in Figure~\ref{fig:sed_spec}) and most of the well-known rest-frame optical emission lines fall within these filters. Nevertheless, most of the filters are wide; thus, these emission lines have limited effect on our SED fitting. Indeed, we checked this by ignoring the emission lines and re-running the SED fitting which resulted in almost identical stellar properties.

We only use the host magnitudes obtained by \jwst\ filters to perform our SED fitting since the reliability of host magnitudes from \hst\ is highly uncertain. 
The SED fitting also requires errors on the magnitudes, which are estimated using the scatter of the magnitude inference from the top-5 ranked PSFs fits. If the scatter is below 0.15 mag, we fix the uncertainty at this value to account for a reported systematic error.
For AEGIS 482 and SDSS1419+5254, we adopt 0.4 mag for the error for F444W filter, since these results are provided by a single PSF.
During the SED fitting process, these errors will be used to assess the posterior probability distribution for SED parameters such as ages, stellar mass, and dust attenuation, and to perform a Markov Chain Monte Carlo routine to constrain the likelihood of these parameters.
For our sample at $z>2$, the seven \jwst\ filters span wavelengths above and below the 4000~\angstrom\ break; thus, the SED fitting should provide a reliable best-fit galaxy template. Unfortunately, SDSS1419 currently only has observations with F200W and F444W, both above the 4000~\angstrom\ break. The SED fits are presented in Figure~\ref{fig:sed_spec} with the exception of SDSS1419. We note that SDSS1420A at $z=1.646$ has a marginal detection with ACS/F814W. As a constraint, we use five times the inferred flux from the F814W filter to set up an upper limit on the SED fit to constrain the strength of the 4000~\angstrom\ break. The host stellar inference, including \smass, SFR, and age, is given at the end of Table~\ref{table:sample}.

We classify the quasar hosts into star-forming and quiescent galaxies using the rest-frame U-V and V-J colors inferred by our model SED fits as done in \citet{vdW+2014}. For reference, we plot galaxy samples from CANDELS~\citep{vdW+2012, vdW+2014} at the equivalent redshifts to our sample (i.e., $1.6<z<3.5$), see Figure~\ref{fig:sizemass} - left. The distribution shows that the quasar hosts are mainly located in a star-forming region. One quasar host is at the boundary, possibly indicating that the host galaxy is close to transitioning to a more quiescent state, likely given its high stellar mass ($\sim2\times10^{11}$ M$_{\odot}$). Broadly, these results are consistent with numerous studies that demonstrate an association between AGN/quasar activity and ongoing star formation over a wide range of cosmic time.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\hspace*{-1cm}  
{\includegraphics[trim={0.6cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/UVJ.png}}&
{\includegraphics[trim={1cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/Mstar-Reff.png}}\\
\end{tabular}
\caption{$Left:$ UVJ diagram for the five quasar systems, together with the sample from CANDELS at $1.6<z<3.5$. Two systems whose 4000~\angstrom\ break is not constrained by \jwst\ are filled in white.
$Right:$ Galaxy size--\smass\ distribution and relations. The \sersic\ index values are presented by the symbol color. For SDSS1420B, \reff\ is labeled using an arrow to indicate an upper limit. We also show the best-fit relation reported in~\citet{vdW+2014} for the star-forming (blue line) and quiescent (red line) at $z\sim2.2$. We also include six broad-line AGNs at $1.6<z<1.7$ from~\citet{Ding2020} based on \hst/WFC3 imaging. 
\label{fig:sizemass}}
\end{figure*}

@@

SDSS1420A is an ideal laboratory to further study high-$z$ quasar hosts since spatially-resolved properties of the stellar population are feasible due to the angular extent of the host, being face-on, and the spatial resolution of multi-band \jwst\ observations. SDSS1420A is a massive disk galaxy ($log$~\smass$\sim11.3$), thus likely to be fully quenched on a short timescale and transition to a bulge-dominated galaxy. Here, our aim is to demonstrate new science capabilities enabled by \jwst. While larger samples will be required to make substantive claims, the CEERS observations of a small quasar sample can already provide further insight into the resolved properties of quasar hosts that have yet to be explored at this redshift and resolution.

@@

\jwst\ has ushered in a new era for which we are now able to study quasar hosts to even higher redshift ($z\sim6$ and beyond) and lower mass. This is crucial to probe epochs closer to the formation of massive galaxies and their supermassive BHs, thus better constraining theoretical models of their connection \citep{Volonteri2021, Ding2022}.
%Kroupa2020\todo{Hi John, Kroupa emailed me to cite this Kroupa2020 which is a comprehensive theory paper. If you feel uncomfortable, you can remove this reference.}

@@

%\bibliography{jwst_hosts}{}
\bibliographystyle{aasjournal}
\input{ding_jwst_v1.bbl}
